Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Abstract formatting
Less background and more specifics in abstract

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (vertical
axis) turbines depend on many parameters: solidity, blade profile, blade pitch,
number of blades, strut drag, operational parameters such as tip speed ratio---and Reynolds number. If numerical models are validated with physical model
data that was obtained at insufficiently high Reynolds numbers, it cannot be
determined whether problems with model predictions are caused by Reynolds
number effects, other turbine parameters or issues with the numerical model.
%It is uncertain whether numerical models validated with physical model data
%obtained at low Reynolds number should be considered validated at all, since
%the scale at which the model will be applied is orders of magnitude larger.
Experiments were performed with a large laboratory-scale cross flow turbine of
to investigate Reynolds number dependence of performance and wake transport
characteristics,
and to determine what an acceptable Reynolds number mismatch is for scaled
physical model tests of cross-flow turbines. It was demonstrated that the
performance of the cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on turbine
diameter of $Re_D \approx 10^6$, or an approximate Reynolds number based on
blade chord of $Re_c \approx 2 \times 10^5$.
A simple model that calculates peak torque coefficient from
static foil data and cross-flow turbine kinematics was shown to be a reasonable
estimator for predicting Reynolds number dependence of an actual cross flow
turbine operating under dynamic conditions.}

@@

\todo[inline]{Rewrite abstract so it is more of a summary of what was done -
tone down the background information a bit. (Note: some background information
was moved to Introduction)}
% %
\todo[inline]{Include a List of Symbols?}

>>>>

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (vertical axis)
    turbines depend on many parameters: solidity, blade profile, blade pitch, number
    of blades, strut drag, operational parameters such as tip speed ratio---and
    Reynolds number. Tolerable mismatch between physical model Reynolds number and
    full-scale Reynolds number was investigated from both the perspective of
    predicting full scale performance and flow dynamics, as well as numerical model
    validation. Experiments were performed with a large laboratory-scale cross flow
    turbine of to investigate Reynolds number dependence of performance and wake
    transport characteristics, and to determine what an acceptable Reynolds number
    mismatch is for scaled physical model tests of cross-flow turbines. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross flow
    turbine operating under dynamic conditions.}

@@

\todo[inline]{Include a List of Symbols?}
